Adolescent well-being in the digital age

### 2022-02-02 timecourses.Rmd
Revise for new RE structure

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(cmdstanr)
library(officer)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(brms)
library(tidyverse)
```

```{r load}
#| cache: false
# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit1 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
    )
  )
```

Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)? And, do changes in well-being correlate with changes in internet adoption (RQ1b)? To answer, we examine Model 1's results.

## Results

Average year-on-year increase in internet adoption

```{r}
tmp <- itu %>% 
  arrange(country, year) %>% 
  group_by(country) %>% 
  mutate(i = internet - lag(internet)) %>% 
  summarise(i = mean(i, na.rm = TRUE))
hist(tmp$i)
percent(mean(tmp$i, na.rm = TRUE))
```

### RQ1a: Temporal trends

Before presenting the time trends, we must calculate the required quantities from the posterior distribution. Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.

```{r calculate-simple-effects}
p_draws <- fits %>%
  mutate(pdraws = map(fit1, pdraws)) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums <- fits %>%
  mutate(psums = map(fit1, psums)) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums_internet <- fits %>%
  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
```

@@

```{r forest-trends}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of linear trends in outcomes. Shaded areas indicate approximate posterior densities of average and region-specific trends. Blue points are country-specific posterior means. Black points and lines are 95%CIs; open points indicate estimates where zero is within the 95% most credible values."
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

@@

::: {.panel-tabset .column-screen-inset-right}
#### All outcomes

# Stack data sets
# Assume all outcomes are proportions (0-1)
dat_all <- bind_rows(
  gwp,
  gbd,
  itu %>% mutate(outcome = "Internet", val = internet)
) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup()

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "5 years",
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title.y = element_blank()
  )
```

#### Life satisfaction

#### Negative experiences

#### Positive experiences

#### Anxiety

#### Depression

#### Self-harm

### RQ1b: Correlations

@@

@@

```{r}
# Display table and print in word document
cor_tab <- cor_pars %>% 
  transmute(
    outcome = str_replace(outcome, "_", " "), 
    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
  )
cor_tab %>%   
  kbl(caption = "Between-country trend correlation parameters") %>% 
  kable_custom()

read_docx() %>% 
  body_add_table(
    cor_tab,
    first_column = TRUE
  ) %>% 
  print("Table-correlations.docx")
```

### Other results from Model 1

#### Shrinkage

>>>>

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(officer)
library(bayestestR)
library(ellipse)
library(ggh4x)
library(mgcv)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(brms)
library(tidyverse)

# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  slice(1:3) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit1 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
    )
  )
```

Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time? And, do changes in well-being correlate with changes in internet adoption? To answer, we examine Model 1's results.

## Data figure

# Stack data sets
# Assume all outcomes are proportions (0-1)
# Draw small multiples figure, outcomes x regions
bind_rows(
  gwp,
  gbd,
  itu %>% mutate(outcome = "Internet", val = internet)
) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "5 years",
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing = unit(4, "pt"),
    axis.title.y = element_blank()
  )
```

```{r}
tmp <- itu %>% 
  arrange(country, year) %>% 
  group_by(country) %>% 
  mutate(i = internet - lag(internet)) %>% 
  summarise(i = mean(i, na.rm = TRUE))
internet_yoy <- percent(mean(tmp$i, na.rm = TRUE), .1)
```

Average year-on-year increase in internet adoption was `r internet_yoy`.

## Main result: Trends

```{r}
get_tab <- function(pattern, label, sort = outcome) {
  fits %>% 
    mutate(
      out = map(
        fit1,
        ~as_draws_df(
          .x, 
          variable = pattern, 
          regex = TRUE
        ) %>% 
          summarise_draws(
            mean, 
            ~quantile2(., probs = c(.025, .975)),
            pd = ~pd(as.numeric(.)), 
            rhat
            )
      )
    ) %>% 
    select(outcome, out) %>% 
    unnest(out) %>% 
    mutate(pd = percent(pd, .1)) %>% 
    arrange({{sort}}) %>% 
    kbl(digits = 2, caption = label) %>% 
    kable_custom()
}

get_tab(
  "b_val_(Intercept|year)$", 
  "Model 1: Population level effects",
  variable
)
```

This table shows the population-level (average across region, country, age) intercepts and time-courses. Negative experiences had increased. We then summarise the region- and country-level trends in a table.

```{r}
get_coeftab <- function(x, group) {
  coef(x, summary = FALSE)[[group]][,,"val_year"] %>% 
    summarise_draws(
      mean, 
      ~quantile2(., probs = c(.025, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}

val_year_region <- fits %>% 
  mutate(out = map(fit1, ~get_coeftab(.x, "region"))) %>% 
  select(outcome, out)
val_year_country <- fits %>% 
  mutate(out = map(fit1, ~get_coeftab(.x, "country"))) %>% 
  select(outcome, out)

bind_rows(
  "region" = val_year_region,
  "country" = val_year_country,
  .id = "Grouping"
) %>% 
  unnest(out) %>% 
  rename(Group = variable) %>% 
  kbl(digits = 2, caption = "Country-specific timecourses") %>% 
  kable_custom() %>% 
  scroll_box("500px")
```

Before presenting the time trends, we must calculate the required quantities from the posterior distribution. Here we calculate posterior samples of region and average-level trends over time, and posterior summaries of trends at all levels.

```{r calculate-simple-effects}
p_draws <- fits %>%
  mutate(pdraws = map(fit1, pdraws)) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums <- fits %>%
  mutate(psums = map(fit1, psums)) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums_internet <- fits %>%
  mutate(psums = map(fit1, ~psums(.x, "internet_year"))) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
```

@@

```{r forest-trends}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of linear trends in outcomes. Shaded areas indicate approximate posterior densities of average and region-specific trends. Blue points are country-specific posterior means. Black points and lines are 95%CIs; open points indicate estimates where zero is within the 95% most credible values."
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 1, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

@@

## Main result: Correlations

@@

# Display table and print in word document
cor_tab <- cor_pars %>% 
  transmute(
    outcome = str_replace(outcome, "_", " "), 
    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
  )
cor_tab %>%   
  kbl(caption = "Between-country trend correlation parameters") %>% 
  kable_custom()

read_docx() %>% 
  body_add_table(
    cor_tab,
    first_column = TRUE
  ) %>% 
  print("Table-correlations.docx")

@@

## Country-specific lines

::: {.panel-tabset .column-screen-inset-right}

### Life satisfaction

### Negative experiences

### Positive experiences

### Anxiety

### Depression

### Self-harm

## Other results

### Shrinkage
